How did Covid-19 affect the number of marriages

### 2024-09-18 paper/paper.qmd
please work

---
title: "How did Covid-19 affect the number of marriages"
subtitle: "Evidence from the Toronto"
author: 
  - Rohan Alexander
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

You can and should cross-reference sections and sub-sections. We use @citeR and @rohan.

@@

Some of our data is of penguins (@fig-bills), from @palmerpenguins.

```{r}
#| label: fig-bills
#| fig-cap: Number of marriage licenses in Toronto, by civic center (2011 - 2024)
#| echo: false

>>>>

---
title: "How did Covid-19 affect the number of marriages"
subtitle: "Evidence from the Toronto"
author: 
  - Rohan Alexander
thanks: "Code and data are available at: https://github.com/RohanAlexander/marriage."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

You can and should cross-reference sections and sub-sections. We use @citeR and @kjlaskjasdnaf.

@@

Some of our data is of penguins (@fig-asdfafdesadfsdfas), from @palmerpenguins.

```{r}
#| label: fig-asdfafdesadfsdfas
#| fig-cap: Number of marriage licenses in Toronto, by civic center (2011 - 2024)
#| echo: false
